The development of children's ability to track and predict turn structure in conversation

### 2015-12-04 paper/Letters/ResponseLetter-Dec2015.tex

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------

\opening{Dear Profs. Dr. Pickering and Dr. Gerrig,}

\smallskip

We resubmit our manuscript on ``The development of children's ability to track and predict turn structure in conversation'' to the \textit{Journal of Memory and Language}. We apologize for our delay in getting the manuscript resubmitted; it took quite a long time to implement one of the suggestions from Reviewer 3, mostly because I had to learn quite a bit of new technical skill to carry his or her suggested analysis out on our computation-heavy data set. In addition to that, we have included a two other follow-up analyses in the Appendix, both inspired by the other reviewers' comments. We have tried to make the text more succinct and the results and discussion sections more distinct and straightforward, following requests from all three reviewers. We hope that, with these changes, we have greatly improved the paper's clarity. Please find a description of specific comments addressed below. Thank you very much for your reconsideration. Please let us know if there is any further information that you require about the submission.

@@

We were concerned about this, too, but we unfortunately did not collect saccadic planning norms for children ages 1--6. We did not feel comfortable (semi-)arbitrarily assigning saccadic planning times to different ages, so in the newly analyzed data we take the conservative approach of using adult-like planning times (200ms) for children at all ages in both experiments.

\smallskip

\noindent \textit{2. The description of the random baseline permutations was not clear.}

\noindent We have tried our best to clarify this description (Section 2.2.2) and have added specific pieces of information where requested.

@@

\smallskip

\noindent \textit{3. Are anticipatory gaze shifts driven by boredom (and not by anticipation)? Do children generally just look away as the speaker goes on?}

\noindent This alternative hypothesis makes a valuable test of what we measured in the experiments. In the Appendix you can now find a graph comparing theoretically boredom-driven lookers and our real lookers. We modeled the proportion of participants looking at the current speaker for our real data and for (fake) boredom-driven lookers (who look away from the current speaker at a constant rate, starting 1 second after the onset of speech) across turns of different length. Even in short turns, where there is very little temporal room for children to behave differently from the boredom-driven lookers, there is a clear difference between the boredom-driven and the real data. (Figure D.2). We take this to mean that children are unlikely to be looking away simply due to boredom.

@@

\smallskip

\noindent \textit{4. The reported results form the models models are hard to follow.}

\noindent We have added a little more information about how each variable was coded and have put summary tables of every model's output into the text.

@@

\bigskip

\noindent \textbf{Reviewer 2}

\noindent \textit{1. It is not clear which claims are backed up by which analyses. Analyses should be carried out for each group separately.}

\noindent Thanks! We have tried to improve the linkage between our claims and analyses and now have presented the statistical results in tables, as requested. Please see responses 4 and 7 under Reviewer 1 for a little more detail. The main focus of our analyses was the effect that age (as a continuous variable) has on anticipatory gaze. However there are two cases in which our main analyses are not satisfying without further, age-group analyses: (a) age sometimes showed itself to interact with other factors (e.g., age and language condition), and (b) without further tests we can not say whether particular age groups themselves statistically differ from chance, across or within conditions. Following your suggestion, we have therefore done two things. First, we added follow-up two-tailed t-tests, making pairwise comparisons between age groups for significant interactions so that we could find out how the interacting factor (e.g., language condition) significantly changes across age groups (Sections B.1--3). Second, we have added individual models of the youngest age groups (ages 1, 2, and 3), comparing their real looking behavior to our randomly permuted data across conditions (at the ends of Sections 2.2.2 and 3.3.2). These follow-up analyses, which are summarized in the text, are primarily described in the Appendix (Section B).

@@

\noindent Our original intention in combining results and discussion was to make the findings easier to understand. Since we were not able to achieve this in the prior submission, we have followed Reviewer 2's advice and now use a more traditional results-only then discussion-only structure. We think that this has improved the clarity of the paper and we give thanks for the suggestion.

\smallskip

\noindent \textit{3. The methods sections need more elaboration in a few places, and the baseline analysis section could be much clearer.}

\noindent We thank the reviewer for his or her careful attention to our methods section (and its missing details.) We have added in the experimental methods information requested and have re-checked each section for missing information someone might need to replicate our methods. We've also worked to clarify the description of the baseline analysis, including a new figure to accompany it (Section 2.2.2; Figure 4). We hope that it is now easier to understand.

@@

\bigskip

\noindent \textbf{Reviewer 3}

\noindent \textit{1. The manuscript could be shortened substantially without loss of content.}

\noindent We agree that the paper was overly long. We have significantly shortened the introduction and tried to remove redundancies where possible in the rest of the text. We have also moved some of the secondary analyses to the Appendix so that the main text can be read without getting into the nitty gritty of every single analysis. We hope that this has helped make the main text more straightforward and approachable length-wise.

@@

\smallskip

\noindent \textit{2. There is a confound between linguistic condition and puppet pair in Experiment 2.}

\noindent We thank Reviewer 3 for this point. We repeat here some of the information now available in the Appendix for easy summary: Our design does not fully cross puppet pair (e.g., robots, blue puppets) with linguistic condition (e.g., ``words only'' and ``no speech''). Even though each puppet pair is associated with different conversation clips across children (e.g. robots talking about kitties, birthday parties, or pancakes), robots were only associated with ``words only'' speech, merpeople were only associated with ``prosody only'' speech, and the puppets with fancy clothes were only associated with the ``no speech'' condition. We did this to increase the pragmatic felicity of the experiments for the older children (i.e., robots make robot sounds, merpeople's voices are muffled under water, the fancy-clothed puppets are in a room with main other voices). It is therefore fair to point out a possible confound between linguistic condition and puppet pair. Thankfully, we also ran a short follow-up study at the museum with 3--5-year-olds in which each child only saw one video---the normal speech conversation about birthday parties---with a randomly assigned puppet pair performing the conversation. Five children watched each puppet pair, for a total of 30 children across the six pairs (shown Figure 3). This experiment holds all things constant except for the appearance of the puppets. We then used a mixed effects logistic regression of children's anticipatory switches (yes or no at each transition), with puppet pair (robots/merpeople/fancy dress/normal-speech-puppets) as a fixed effect and participant and turn transition as random effects. In four versions of this model we systematically varied the reference level to check for differences between every puppet pair, finding no significant affects of puppet type on switching rate. We take this as evidence that, although we did not fully cross puppet pairs and linguistic conditions in Experiment 2, it was unlikely to have had strong effects on children's looking rates above and beyond the intended effects of linguistic condition. We have included details and graphs for this analysis in the Appendix.

@@

\noindent We completely agree with the reviewer on this point. We did not have the ability to create custom animated conversation videos at the time. But, since then, the first author has developed a method for doing exactly that. Unfortunately, for this past work, we are still stuck with the puppet stimuli.

\smallskip

\noindent \textit{4. The model design needs to be further justified and the way the effects are talked about needs clarification.}

\noindent We corrected small mistakes in the model description (thanks for spotting them!), for example, making it clear that we used a logistic regression (for our binary response variable of switch-no switch) and have added short bits of information justifying our use of separate models for adults and children and our use of random slopes. We have also cleaned up the way we talk about the significant effects in the model output because they were sometimes misleading. There was no concern about dummy coding since this is carried out automatically across factor predictors by the glmer package in R (as is now clearer with the presentation of results in Tables 2 and 5).

@@

\noindent We really liked this suggestion but felt that it was too far outside the scope of the current paper, especially because our stimulus set is probably too small to build a generalizable model of cue usefulness. We will, however, seriously consider this type of analysis for future work, with adult and child turn-taking, in experiments and in spontaneous speech corpora.

\smallskip

\noindent \textit{6. The random baseline would be better if it were converted to a full permutation analysis so that the baseline rate of anticipatory gazing is not treated as an additive factor, which it probably is not.}

\noindent We thank Reviewer 3 very much for his/her suggestion and clear explanation of how to conduct the analysis. To be sure about the results we decided to run 5,000 random permutations on the data from each experiment, resulting in 20,000 glmer runs. We apologize for the delay of this resubmission, which is primarily due to the implementation of this random permutation analysis. To analyze our data on this scale, the first author had to learn some new R libraries, optimization techniques, and how to use the local computer cluster, dealing with many technical problems along the way! That being said, we think that the new permutation analysis is indeed simpler and more theoretically intuitive than our prior method (described in 2.2.2 and 3.3.2, visualized in Section A). Please note that there were two problems with conducting the analyses as originally instructed in the reviewer's comments: (a) we used \textit{t} values instead of \textit{$\beta$} estimates because the standard error estimates for the randomly permuted data were nearly categorically higher, dramatically so in some cases, and (b) many of the models (especially in Experiment 2) resulted in convergence warnings, which we have dealt with by only reporting results for converging models.

@@

\smallskip

\noindent \textit{7. The theoretical contribution of this paper is not clear.}

\noindent We have tried to improve the clarity of our findings' theoretical importance in the revised manuscript. I summarize here the points that we cover. One of the most important theoretical contributions of our work is in establishing and replicating speech act effects in children and adults' spontaneous predictions---while participants may always use linguistic information to predict upcoming speaker changes, our results to not support the idea that they always use linguistic information to predict upcoming turn ends, as is assumed in metalinguistic measures of turn-end prediction (e.g., pressing a button while listening to speech). Our results suggest that participants' spontaneous predictions are the result of question-monitoring, presumably achieved by recruiting linguistic cues to questionhood from the unfolding signal. The trends in our data suggest that participants are primarily recruiting lexical cues to do this, though establishing this pattern will require follow up work with more focused stimuli.

A second, but related theoretical takeaway is that lexical information alone is not equivalent to full linguistic information for children, as it has been shown to be (e.g., de Ruiter et al., 2006) and replicated here (Tables 2 and 5) with adults. If this effect arose in our data because children do not respond well to phonetically manipulated speech in conversational contexts, this point can be overturned by work that controls linguistic information through other means. If not, it suggests that there is something specially informative about the combined prosodic-lexical marking on question turns, for which there is also prior support (Torreira et al., 2015) though our finding would be the first to show such effects developmentally.

A third theoretical contribution is that young children (e.g., at ages one and two) do make anticipatory gaze prediction more often than would be expected by chance alone, but not by much. Since older children and adults' gaze shifts are primarily driven by question turns, this may suggest that, although children \textit{can} make predictions about upcoming turn structure, it doesn't count for much until they have acquired the linguistic skill to pick out question turns. This finding, in turn, has potentially important implications for how participant role (first- instead of third-person) and cultural differences (high vs. low parent-infant interaction styles) might affect children's early predictive skill. It also bridges prior work demonstrating that children begin taking non-linguistic turns in infancy (e.g., Hilbrink et al., 2015), but still have trouble integrating linguistic aspects of responding at age 3--4 (Casillas et al., in press; Garvey \& Berninger, 1984).

### 2015-12-04 paper/CasillasFrank-Anticip.tex
resubmitted

\journal{}

@@

Our findings suggest that children and adults use linguistic cues to make predictions about upcoming turn structure, but that they primarily do so to predict speaker transitions after a question. We also find that children make more predictions than  expected by chance, even at age XX, but that it takes several years before they recruit linguistic cues to anticipate responses more often after questions. We found no direct evidence of an early prosody advantage in children's anticipations and, further, no evidence that prosodic or lexical cues alone can substitute for their combination in the full linguistic signal, as is proposed for adults \citep{de-ruiter2006}.

@@

Our baseline analyses revealed that none of the significant predictors from models of the original, turn-related data can be explained by random looking (see Figures \ref{fig:E1-ChiTs} and \ref{fig:E1-AduTs} for the full distributional data). For the children's data, the original \textit{t}-values for language condition, gap duration, the age-language condition interaction, and the language condition-transition type interaction were all greater than 95\% of \textit{t}-values for the randomly permuted data (99.9\%, 95.5\%, 99.4\%, and 96\%, respectively). Similarly, the adults' data showed significant differentiation from the randomly permuted data for two of the three originally significant predictors---transition type and the transition type-gap duration interaction (greater than 99.9\% and 99.7\% of random \textit{t}-values, respectively)---with marginal differentiation for the interaction of language condition and transition type (greater than 94.7\% of random \textit{t}-values).

@@

\begin{scriptsize}
\begin{longtable}{lcccl}
  \textbf{\textit{Children}} &&&& \\
    \hline
                       & Estimate & Std. Error & z value & Pr($>$$|$z$|$)    \\
    \hline
    (Intercept)                & -3.57414  &   0.48576 &  -7.358 & 1.87e-13 ***    \\
    Age                         & 0.02543 &    0.10260  &  0.248   & 0.8042        \\
    Type$=$\textit{non-Question}                      & -0.81873  &   0.59985 &  -1.365  &  0.1723        \\
    Duration                   &  4.17672  &   0.62446  &  6.689 & 2.25e-11 ***    \\
    Age*Type$=$\textit{non-Question}                &    0.15116   &  0.13643  &  1.108  &  0.2679        \\
	\hline
    Condition$=$\textit{normal}            &  0.36710 &    0.43296 &   0.848  &  0.3965        \\
    Age*Condition$=$\textit{normal}       &   0.12919 &    0.10227  &  1.263  &  0.2065        \\
    Condition$=$\textit{normal}*     &   0.91059  &   0.72095  &  1.263 &   0.2066        \\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
    Age*Condition$=$\textit{normal}* &   -0.37542  &   0.16963  & -2.213 &   0.0269 *      \\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
	\hline
    Condition$=$\textit{muffled}         &   -1.63429  &   0.86390 &  -1.892   & 0.0585 .      \\
    Age*Condition$=$\textit{muffled}       &   0.39317 &     0.18907 &   2.080  &  0.0376 *      \\
    Condition$=$\textit{muffled}*     &  1.77190  &   1.24864  &  1.419 &   0.1559        \\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
    Age*Condition$=$\textit{muffled}* &  -0.47057 &    0.28703 &  -1.639 &   0.1011        \\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
	\hline
    Condition$=$\textit{robot}            &  -0.26741 &    0.59071 &  -0.453  &  0.6508        \\
    Age*Condition$=$\textit{robot}           &   0.13740  &   0.13568   & 1.013  &  0.3112        \\
    Condition$=$\textit{robot}*     &   -1.02193  &   1.01227  & -1.010  &  0.3127        \\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
    Age*Condition$=$\textit{robot}*  &   0.08946  &   0.22349   & 0.400 &   0.6890        \\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\

    \hline
  &&&& \\
  \textbf{\textit{Adults}} &&&& \\
    \hline
                       &  Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\    
    \hline
    (Intercept)           &  -3.4557   &   0.7199 &  -4.800 & 1.58e-06 *** \\ 
    Type$=$\textit{non-Question}                  &   0.4292  &    0.6089  &  0.705 & 0.480916     \\ 
    Duration             &     4.7500   &   1.2480  &  3.806 & 0.000141 *** \\ 
	\hline
    Condition$=$\textit{normal}    &      1.2556   &   0.5633  &  2.229 & 0.025805 *   \\ 
    Condition$=$\textit{normal}* &   -0.9452  &    0.7631 &  -1.239 & 0.215475     \\ 
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
	\hline
    Condition$=$\textit{muffled}     &     0.3349  &    0.8965  &  0.374 & 0.708692     \\ 
    Condition$=$\textit{muffled}*  &  0.6627  &    1.2138 &   0.546 & 0.585108     \\ 
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
	\hline
    Condition$=$\textit{robot}       &     1.5938  &    0.7208 &   2.211 & 0.027023 *   \\ 
    Condition$=$\textit{robot}*   &  -1.1265  &    0.9109  & -1.237 & 0.216201     \\ 
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
    \hline
    &&&& \\
  \caption{Model output for children and adults' anticipatory gaze switches.}
\label{tab:E2-models}
\end{longtable}
\end{scriptsize}

@@

\begin{figure}[!htb]
\begin{center}
\includegraphics[width=0.9\textwidth]{figures/E2-child-randvsreal-ttest-normaltypesages.png}
\end{center}
\caption{Significant pairwise comparisons of the \textit{normal speech}-\textit{no speech} language condition effect for questions status, across ages, in Experiment 2.} 
\label{fig:E2-lgagetypeinteraction}
\end{figure}

\section{Non-convergent models}
\setcounter{figure}{0}

>>>>

\linespread{2}
\journal{}

@@

Our findings suggest that children and adults use linguistic cues to make predictions about upcoming turn structure, but that they primarily do so to predict speaker transitions after a question. We also find that children make more predictions than expected by chance at age two, but that it takes several years before they recruit linguistic cues to anticipate responses more often after questions. We found no direct evidence of an early prosody advantage in children's anticipations and, further, no evidence that prosodic or lexical cues alone can substitute for their combination in the full linguistic signal, as is proposed for adults \citep{de-ruiter2006}.

@@

Our baseline analyses revealed that none of the significant predictors from models of the original, turn-related data can be explained by random looking (see Figures \ref{fig:E1-ChiTs} and \ref{fig:E1-AduTs} for the full distributional data). For the children's data, the original \textit{t}-values for language condition, gap duration, the age-language condition interaction, and the language condition-transition type interaction were all greater than 95\% of \textit{t}-values for the randomly permuted data (99.9\%, 95.5\%, 99.4\%, and 96\%, respectively). Similarly, the adults' data showed significant differentiation from the randomly permuted data for two of the three originally significant predictors---transition type and the transition type-gap duration interaction (greater than 99.9\% and 99.7\% of random \textit{t}-values, respectively)---with marginal differentiation for the interaction of language condition and transition type (greater than 94.6\% of random \textit{t}-values).

@@

\begin{scriptsize}
\begin{longtable}{lcccl}
  \textbf{\textit{Children}} &&&& \\
    \hline
                       & Estimate & Std. Error & z value & Pr($>$$|$z$|$)    \\
    \hline
    (Intercept)                & -3.57414  &   0.48576 &  -7.358 & 1.87e-13 ***    \\
    Age                         & 0.02543 &    0.10260  &  0.248   & 0.8042        \\
    Type$=$\textit{non-Question}                      & -0.81873  &   0.59985 &  -1.365  &  0.1723        \\
    Duration                   &  4.17672  &   0.62446  &  6.689 & 2.25e-11 ***    \\
    Age*Type$=$\textit{non-Question}                &    0.15116   &  0.13643  &  1.108  &  0.2679        \\
	\hline
    Condition$=$\textit{normal}            &  0.36710 &    0.43296 &   0.848  &  0.3965        \\
    Age*Condition$=$\textit{normal}       &   0.12919 &    0.10227  &  1.263  &  0.2065        \\
    Condition$=$\textit{normal}*     &   0.91059  &   0.72095  &  1.263 &   0.2066        \\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
    Age*Condition$=$\textit{normal}* &   -0.37542  &   0.16963  & -2.213 &   0.0269 *      \\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
	\hline
    Condition$=$\textit{prosody}         &   -1.63429  &   0.86390 &  -1.892   & 0.0585 .      \\
    Age*Condition$=$\textit{prosody}       &   0.39317 &     0.18907 &   2.080  &  0.0376 *      \\
    Condition$=$\textit{prosody}*     &  1.77190  &   1.24864  &  1.419 &   0.1559        \\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
    Age*Condition$=$\textit{prosody}* &  -0.47057 &    0.28703 &  -1.639 &   0.1011        \\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
	\hline
    Condition$=$\textit{words}            &  -0.26741 &    0.59071 &  -0.453  &  0.6508        \\
    Age*Condition$=$\textit{words}           &   0.13740  &   0.13568   & 1.013  &  0.3112        \\
    Condition$=$\textit{words}*     &   -1.02193  &   1.01227  & -1.010  &  0.3127        \\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
    Age*Condition$=$\textit{words}*  &   0.08946  &   0.22349   & 0.400 &   0.6890        \\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\

    \hline
  &&&& \\
  \textbf{\textit{Adults}} &&&& \\
    \hline
                       &  Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\    
    \hline
    (Intercept)           &  -3.4557   &   0.7199 &  -4.800 & 1.58e-06 *** \\ 
    Type$=$\textit{non-Question}                  &   0.4292  &    0.6089  &  0.705 & 0.480916     \\ 
    Duration             &     4.7500   &   1.2480  &  3.806 & 0.000141 *** \\ 
	\hline
    Condition$=$\textit{normal}    &      1.2556   &   0.5633  &  2.229 & 0.025805 *   \\ 
    Condition$=$\textit{normal}* &   -0.9452  &    0.7631 &  -1.239 & 0.215475     \\ 
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
	\hline
    Condition$=$\textit{prosody}     &     0.3349  &    0.8965  &  0.374 & 0.708692     \\ 
    Condition$=$\textit{prosody}*  &  0.6627  &    1.2138 &   0.546 & 0.585108     \\ 
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
	\hline
    Condition$=$\textit{words}       &     1.5938  &    0.7208 &   2.211 & 0.027023 *   \\ 
    Condition$=$\textit{words}*   &  -1.1265  &    0.9109  & -1.237 & 0.216201     \\ 
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
    \hline
    &&&& \\
  \caption{Model output for children and adults' anticipatory gaze switches.}
\label{tab:E2-models}
\end{longtable}
\end{scriptsize}

@@

\begin{figure}[!htb]
\begin{center}
\includegraphics[width=0.9\textwidth]{figures/E2-child-randvsreal-ttest-normaltypesages.png}
\end{center}
\caption{Significant pairwise comparisons of the \textit{normal speech}-\textit{no speech} language condition effect for transition type, across ages, in Experiment 2.} 
\label{fig:E2-lgagetypeinteraction}
\end{figure}

\section{Non-convergent models}
\setcounter{table}{0}

Non-convergent models made up 22--24\% of the 5,000 models of randomly permuted data in Experiment 1 and 69--70\% of the 5,000 for Experiment 2. We excluded these non-convergent models because they displayed erratic $\beta$ and \textit{SE} estimates, as summarized below in the table of \textit{t}-values from convergent and non-convergent models in Experiment 1. The non-convergent models from Experiment 2 showed similar patterns. The high frequency of problematic models persisted even when we changed optimizers and we suspect the issue derives from data sparsity in some of the random runs.

\begin{table}[h]
  \begin{scriptsize}
\centering
  \begin{tabular}{lccccc}
    Variable & Mean & Median & \textit{SD} & Minimum & Maximum\\ 
    \hline
	\textbf{\textit{Children}} &&&&& \\
    \hline
    (Intercept)						&	-2.52 (-458.42)	& -2.54 (-2.86)	& 0.87 (1319.22)		& -5.53 (-8185.36)	& 0.41 (0.97)			\\
    Age								& -0.51 (-17.83)		& -0.49 (-0.53)	& 0.79 (83.78)		& -3.71 (-672.2)		& 2.3 (342.8)			\\
    LgCond					& -0.53 (-109.91)		& -0.55 (-0.63)	& 0.93 (564.42)		& -3.93 (-4418.74)	& 3.23 (2296.19)		\\
    Type							& -0.10 (-29.66)		& -0.09 (-0.1)		& 0.98 (515.12)		& -4.06 (-4383.92)	& 3.23 (2296.19)		\\
    Duration						& 0.99 (345.53)		& 0.98 (1.15)		& 1.07 (1323.13)		& -2.44 (-5048.24)	& 3.36 (3416.68)		\\
    Age*LgCond				& 0.19 (10.64)		& 0.2 (0.18)		& 0.9 (109.6)			& -3.31 (-581.61)		& 5.78 (9985.16)		\\
    Age*Type						& 0.02 (-1.8)			& 0.001 (-0.05)	& 0.9 (98.27)			& -3.36 (-884.36)		& 3.59 (946.81)		\\
    LgCond*Type			& 0.2 (45.32)			& 0.2 (0.27)		& 0.96 (691.3)		& -3.12 (-4160.06)	& 3.45 (640.43)		\\
    Age*LgCond*Type		& -0.12 (-14.23)		& -0.12 (-0.15)	& 0.93 (156.72)		& -2.98 (-1318.26)	& 3.39 (5107.64)		\\
    \hline
	\textbf{\textit{Adults}} &&&&& \\
    \hline
    (Intercept)    					&    -1.63 (-126.14) 	& -1.71 (-1.73)	& 0.97 (713.39)		& -4.08 (-12111.22)	& 2.15 (649.55)		\\
    LgCond  					&      -0.26 (-679.6) 	& -0.3 (-0.53)		& 1.02 (15894.33)	& -3.45 (-494979.7)	& 3.35 (88581.58)	\\
    Type 							&       -0.11 (6.29) 	& -0.13 (-0.04)	& 1.11 (501.5)		& -3.85 (-6420.76)	& 3.28 (8177.88)		\\
    Duration  						&       0.25 (84.09) 	& 0.27 (0.26)		& 1.1 (1152.94)		& -3.25 (-10864.51)	& 3.46 (18540.62)	\\
    LgCond*Type  			&       0.12 (-242.27) 	& 0.1 (0.34)		& 1.07 (26836.7)		& -3.41 (-62264.27)	& 3.81 (509198.4)	\\
    LgCond*Duration  		&       0.15 (780.03) 	& 0.16 (0.39)		& 1.04 (44105.02)	& -3.84 (-798498.6)	& 3.55 (1145951)		\\
    Type*Duration 				&        0.05 (-6.56) 	& 0.05 (0.02)		& 1.13 (1389.9)		& -3.54 (-15979.22)	& 3.87 (16419.46)	\\
    LgCond*Type*Duration  &      -0.06 (1083.63)	& -0.08 (-0.21)	& 1.1 (63116.54)		& -4.21 (-1201895)	& 4.02 (1284965)		\\
    \hline
  \end{tabular}
  \caption{Estimated \textit{t}-values for each predictor in in the adult and child models from Experiment 1. Converging (`C') and non-converging (`non-C') values are shown as: `C (non-C)'. }
\label{tab:nonconv_e1}
 \end{scriptsize}
\end{table}

\section{Miscellaneous}
\setcounter{figure}{0}

One alternative hypothesis for children's anticipatory gazes is that they simply grow bored and start looking away at a constant rate after a turn begins. This data plotted here show a hypothetical group of participants who begin to lose interest (at a linear rate) after one second of a turn (gray dots) compared to participants' real data from Experiment 2 (black dots). This pattern suggests that, though children do look away with time, their looks away are not simply driven by boredom.

\begin{figure}[!htb]
\begin{center}
\includegraphics[width=0.9\textwidth]{figures/boredom-hypothesis.png}
\end{center}
\caption{Proportion participants looking at the current speaker: hypothetical boredom-driven data (gray dots) versus real data from Experiment 2 (black dots).} 
\label{fig:boredomhypothesis}
\end{figure}

\bigskip

The design for Experiment 2 does not fully cross puppet pair (e.g., robots, blue puppets) with linguistic condition (e.g., ``words only'' and ``no speech''). Even though each puppet pair is associated with different conversation clips across children (e.g. robots talking about kitties, birthday parties, or pancakes), robots were only associated with ``words only'' speech, merpeople were only associated with ``prosody only'' speech, and the puppets with fancy clothes were only associated with the ``no speech'' condition. We did this to increase the pragmatic felicity of the experiments for the older children (i.e., robots make robot sounds, merpeople's voices are muffled under water, the fancy-clothed puppets are in a room with main other voices). It is therefore fair to point out a possible confound between linguistic condition and puppet pair. Thankfully, we also ran a short follow-up study at the museum with 3--5-year-olds in which each child only saw one video---the normal speech conversation about birthday parties---with a randomly assigned puppet pair performing the conversation. Five children watched each puppet pair, for a total of 30 children across the six pairs. This experiment holds all things constant except for the appearance of the puppets. We then used a mixed effects logistic regression of children's anticipatory switches (yes or no at each transition), with puppet pair (robots/merpeople/fancy dress/other-3; Figure \ref{fig:speakers}) as a fixed effect and participant and turn transition as random effects. In four versions of this model we systematically varied the reference level to check for differences between every puppet pair, finding no significant affects of puppet type on switching rate. We take this as evidence that, although we did not fully cross puppet pairs and linguistic conditions in Experiment 2, it was unlikely to have had strong effects on children's looking rates above and beyond the intended effects of linguistic condition.

\begin{figure}[!htb]
\begin{center}
\includegraphics[width=0.9\textwidth]{figures/all-puppetdyads-bars.png}
\end{center}
\caption{Proportion gaze switches across puppet pairs when linguistic condition and conversation are held constant.} 
\label{fig:pairconfound}
\end{figure}
